Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-11 paper.qmd
tinkering with the code

umap_scurve_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = umap_scurve, 
                                    x = "UMAP1", y = "UMAP2"))) |>
  rename(c("UMAP1" = "scaled_UMAP1", 
                  "UMAP2" = "scaled_UMAP2")) |>
  mutate(ID = 1:NROW(umap_scurve))

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  coord_fixed() +
  interior_annotation_left("a")
```

@@

hex_grid_scurve <-  ggplot(data = hex_grid_with_counts, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  coord_fixed() +
  interior_annotation_left("b")
```

@@

hex_grid_nonempty_scurve <-  ggplot(data = hex_grid_nonempty, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = df_bin_centroids, aes(x = c_x, y = c_y), color = "#33a02c") +
  coord_fixed() +
  interior_annotation_left("c") 
```

>>>>

ar <- umap_scurve |>
  summarise_at(c("UMAP1", "UMAP2"), 
    function(x) max(x)-min(x)) |>
  mutate(ar = UMAP2/UMAP1) |>
  pull(ar) # This is a bit cumbersome too
hr <- 2/sqrt(3)
umap_scurve_scaled <- umap_scurve |>
  mutate_at(c("UMAP1", "UMAP2"), 
    function(x) (x - min(x))/(max(x)-min(x))) |> # can be no missings
  mutate(UMAP2 = UMAP2 * ceiling(ar/hr) * hr)

  #as.data.frame(do.call(cbind, gen_scaled_data(data = umap_scurve, 
  #                                  x = "UMAP1", y = "UMAP2"))) |>
  #rename(c("UMAP1" = "scaled_UMAP1", 
  #                "UMAP2" = "scaled_UMAP2")) |>
  #mutate(ID = 1:NROW(umap_scurve))

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  #coord_fixed() +
  xlim(c(-0.3, 1.3)) + ylim(c(-0.3, 2.6)) +
  interior_annotation_left("a")
```

@@

hex_grid_scurve <-  ggplot(data = hex_grid_with_counts, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  #coord_fixed() +
  xlim(c(-0.3, 1.3)) + ylim(c(-0.3, 2.6)) +
  interior_annotation_left("b")
```

@@

hex_grid_nonempty_scurve <-  ggplot(data = hex_grid_nonempty, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = df_bin_centroids, aes(x = c_x, y = c_y), color = "#33a02c") +
  #coord_fixed() +
  xlim(c(-0.3, 1.3)) + ylim(c(-0.3, 2.6)) +
  interior_annotation_left("c") 
```
